% !TEX TS-program = pdflatexmk
\documentclass[11pt,a4paper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{banking}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}    % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page

\makeatletter
\renewcommand*{\nopagenumbers}{\@displaypagenumbersfalse}
\AtEndPreamble{
  \AtBeginDocument{
    \if@displaypagenumbers
      \@ifundefined{r@lastpage}{}{
        \ifthenelse{\pageref{lastpage}>1}{
          \settowidth{\pagenumberwidth}{\color{color2}\addressfont\itshape\strut\thepage/\pageref{lastpage}}
          \fancypagestyle{plain}{
            \fancyfoot[r]{\parbox[t]{\pagenumberwidth}{\color{color2}\addressfont\itshape\strut\thepage}}}% the parbox is required to ensure alignment with a possible center footer (e.g., as in the casual style)
          \pagestyle{plain}}{}}
      \AtEndDocument{\label{lastpage}}\else\fi}}
\makeatother

% character encoding
%\usepackage[utf8]{inputenc}                  % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                         % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=.75]{geometry}
%\setlength{\hintscolumnwidth}{3cm}           % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}      % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...


% personal data
\firstname{Adam}
\familyname{Liter}
%\title{Vita}                          % optional, remove / comment the line if not wanted
\address{\textbf{School}: 121 Beal St., East Lansing, MI 48823}{\textbf{Permanent}: 18886 Magenta Bay, Eden Prairie, MN 55347}    % optional, remove / comment the line if not wanted
\mobile{+1~(952)~807~5616}                     % optional, remove / comment the line if not wanted
%\phone{+2~(345)~678~901}                      % optional, remove / comment the line if not wanted
%\fax{+3~(456)~789~012}                        % optional, remove / comment the line if not wanted
\email{literada@msu.edu}                          % optional, remove / comment the line if not wanted
%\homepage{}                    % optional, remove / comment the line if not wanted
\extrainfo{{\Large \ComputerMouse}  \href{http://www.msu.edu/~literada}{www.msu.edu/$\sim$literada}}            % optional, remove / comment the line if not wanted
%\photo[64pt][0pt]{10_8A.jpg}                  % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                            % optional, remove / comment the line if not wanted

% to show numerical labels in the bibliography (default is to show no labels); only useful if you make citations in your resume
%\makeatletter
%\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
%\makeatother

% bibliography with multiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\usepackage{fancyhdr}
\usepackage{enumitem}

\makeatletter
\def\@biblabel#1{}
\makeatother

\newlength{\bibhang}
\setlength{\bibhang}{.25in}

\usepackage{etoolbox}
\patchcmd{\thebibliography}{%
  \advance\leftmargin\labelsep
}{%
  \advance\leftmargin\labelsep
  \advance\leftmargin\bibhang
  \itemindent-\bibhang
}{}{}

\usepackage{multibib}
\newcites{ref}{Refereed Articles}
\usepackage[colorlinks]{hyperref}
\begin{document}
\hypersetup{urlcolor=black}
\lfoot{\color{color2}\addressfont\itshape\strut Last Updated: \today}
%\begin{CJK*}{UTF8}{gbsn}                     % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle
\hypersetup{urlcolor=blue}
\section{Education}
\cventry{}{Michigan State University}{M.A., Linguistics}{01/2013 -- (expected:) 05/2015}{\textit{East Lansing, MI}}{\footnotesize{Cumulative GPA: 4.0}}
\cventry{}{Michigan State University}{B.A., Linguistics (Honors) \& B.A., Philosophy (Honors)}{08/2010 -- (expected:) 05/2014}{\textit{East Lansing, MI}}{\footnotesize{\begin{itemize} \item Cognitive Science Specialization \item Women's and Gender Studies Minor \end{itemize}Dean's List (Fall 2010 -- Present); Cumulative GPA: 4.0}}
% arguments 3 to 6 can be left empty
%\cventry{}{University of Michigan}{2013 Linguistics Institute Student}{06/2013 -- 07/2013}{\textit{Ann Arbor, MI}}{\footnotesize{Courses taken:\begin{itemize} \item Prosody and Information Structure (w/Angelika Kratzer \& Lisa Selkirk) \item Python 3 for Linguists (w/Damir Cavar \& Malgorzata Cavar) \item Intensional Semantics (w/Ezra Keshet) \item Agreement and Word Order in Minimalist Syntax (w/Vicki Carstens) \end{itemize}Cumulative GPA:}}
\cventry{}{University of Minnesota -- Twin Cities}{Non-Degree Seeking Student}{09/2007 -- 05/2010}{\textit{Minneapolis, MN}}{\footnotesize{\begin{itemize}\item Post-Secondary Enrollment Options ('09 -- '10) \item University of Minnesota Talented Youth Mathematics Program ('07 -- '09) \end{itemize}Cumulative GPA: 3.911}}
\cventry{}{Eden Prairie High School}{High School Diploma}{09/2006 -- 06/2010}{\textit{Eden Prairie, MN}}{\footnotesize{Cumulative GPA: 3.99}}

%\section{Theses}
%\cvitem{M.A., Linguistics, Thesis}{\emph{Title} [\href{http://www.msu.edu/~literada}{PDF}]}
%\cvitem{Committee}{Supervisors}
%\cvitem{Abstract}{Short thesis abstract}
%\cvitem{B.A., Linguistics, Thesis}{\emph{Title} [\href{http://www.msu.edu/~literada}{PDF}]}
%\cvitem{Supervisors}{Alan Munn}
%\cvitem{Abstract}{Short thesis abstract}
%\cvitem{B.A., Philosophy, Thesis}{\emph{Title} [\href{http://www.msu.edu/~literada}{PDF}]}
%\cvitem{Supervisors}{Kristie Dotson}
%\cvitem{Abstract}{Short thesis abstract}

\section{Honors \& Awards}
\subsection{Funded Awards}
\cventry{}{College of Arts and Letters}{Undergraduate Research Initiative -- Grantee}{10/2012 -- present}{\textit{Michigan State University, East Lansing, MI}}{}
\cventry{}{Honors College}{University Distinguished Scholarship}{08/2010 -- present}{\textit{Michigan State University, East Lansing, MI}}{}
\cventry{}{Michigan State University}{National Merit Scholar}{08/2010 -- present}{\textit{East Lansing, MI}}{}
\cventry{}{Honors College}{Professorial Assistantship}{08/2010 -- 05/2012}{\textit{Michigan State University, East Lansing, MI}}{}
\subsection{Undergraduate Conference Presentation Awards}
\cventry{}{UURAF}{Category Winner (with C. Heffner)}{04/2012}{\textit{Michigan State University, East Lansing, MI}}{}
\cventry{}{MSULC}{Award Winner, Poster Presentation (with C. Heffner)}{04/2012}{\textit{Michigan State University, East Lansing, MI}}{}

\section{Research Experience}
\cventry{}{\href{http://msuacquisition.wordpress.com/}{MSU Language Acquisition Lab}}{Lab Assistant for Cristina Schmitt, Ph.D.}{06/2012 -- present}{\textit{Michigan State University, East Lansing, MI}}{\footnotesize{I now manage the artificial language experiment investigating the acquisition of a unique nominal number system.}}
\cventry{}{\href{http://msuacquisition.wordpress.com/}{MSU Language Acquisition Lab}}{Professorial Assistant for Cristina Schmitt, Ph.D.}{08/2010 -- 06/2012}{\textit{Michigan State University, East Lansing, MI}}{\footnotesize{I am involved in an artificial language experiment investigating the acquisition of a unique nominal number system.}}

% Publications from a BibTeX file using the multibib package
\section{Publications}
%\renewcommand{\refname}{Refereed Articles}
%\nociteref{*}
%\bibliographystyleref{apalike2-cv}
%\bibliographyref{cvpubsref}
\renewcommand{\refname}{Non-Refereed Articles}
\nocite{*}
\bibliographystyle{apalike2-cv}
\bibliography{cvpubsnonref}              % 'publications' is the name of a BibTeX file

\section{Conference Presentations}
\newenvironment{fakebib}
{\par\leftskip=0.25in \parindent=-\leftskip}
{\par}
\begin{fakebib}
Liter, A. (2012, November). Facebook's Facility for Necessary (Political) Identities: A case study of asymmetric moral and epistemic standings. Paper presented at  7th Annual Southern Illinois University Edwardsville Undergraduate Philosophy Conference. 

Heffner, C., Liter, A., \& Schmitt, C. (2012, April). Lions, zebras, and plurals, oh my!: Learning a novel number system. Poster presented at:
\begin{itemize}[leftmargin=.25in]
\item The third annual Michigan State Undergraduate Linguistics Conference (MSULC), East Lansing, MI.
\item The University Undergraduate Research and Arts Forum 2012 (UURAF), East Lansing, MI.
\end{itemize}

Heffner, C., Liter, A., \& Schmitt, C. (2011, April). Dogs not put in boxes by boys: Learning a novel number system. Poster presented at:
\begin{itemize}[leftmargin=.25in]
\item The first annual Great Lakes Expo for Experimental and Formal Undergraduate Linguistics (GLEEFUL), East
Lansing, MI.
\item The second annual Michigan State Undergraduate Linguistics Conference (MSULC), East Lansing, MI.
\item The University Undergraduate Research and Arts Forum 2011 (UURAF), East Lansing, MI.
\end{itemize}

Liter, A., (2011, April). Towards a Theoretical Tool against Anthropogenic Environmental Harm: Bringing the Western ``Bio-logic'' into View. Paper presented at at the University Undergraduate Research and Arts Forum 2011 (UURAF), East Lansing, MI. %\\ \\

%For selected PDFs of papers and handouts in various states of progress, click \href{http://www.msu.edu/~literada/papers.html}{here}.
\end{fakebib}

\section{Professional Service}
\cventry{}{\href{http://stance.iweb.bsu.edu/}{Stance}}{Assistant Editorial Board Member}{2012 -- 2013}{\textit{Ball State University, Munice, IN}}{\footnotesize{I served as an external reviewer for this professional, annual undergraduate philosophy journal.}}
\cventry{}{\href{https://www.msu.edu/~qualms/qUALMS/Home.html}{qUALMS}}{President}{08/2012 -- present}{\textit{Michigan State University, East Lansing, MI}}{\footnotesize{I run the ``q Undergraduate Association for Linguistics at Michigan State'', which consists of preparing programming for throughout the year, arranging speakers and activities for the club, and advertising for linguistics on campus.}}
\cventry{}{\href{https://www.msu.edu/~qualms/qUALMS/Conferences.html}{GLEEFUL}}{Chair ('13), Vice Chair ('11 \& '12)}{04/2011, 04/2012, \& (in prep:) 04/2013}{\textit{Michigan State University, East Lansing, MI}}{\footnotesize{This year, I will organize the Great Lakes Expo for Experimental and Formal Undergraduate Linguistics, an international undergraduate linguistics conference. I will manage advertising, volunteers, fundraising, review of abstracts, the arrangement of the program, the arrangement of homestays and transportation, and the keynote speaker. In '11 and '12, I aided Chris Heffner in running the conference.}}
\cventry{}{\href{https://www.msu.edu/~qualms/qUALMS/Conferences.html}{MSULC}}{Vice Chair ('13), Chair ('11 \& '12)}{04/2011, 04/2012, \& (in prep:) 04/2013}{\textit{Michigan State University, East Lansing, MI}}{\footnotesize{In '11 and '12, I advertised for the Michigan State Undergraduate Linguistics Conference, a conference for MSU linguistics students only. I raised funds, collected abstracts, booked rooms, and ran the conference. This year, I will aid Haley Rooney in organizing the conference.}}

\section{Skills}
\subsection{Languages}
\cvlistitem{English (specifically, \href{http://en.wikipedia.org/wiki/North_Central_American_English}{North-Central American English}) -- native}
\cvlistitem{German -- nearly fluent}
\cvlistitem{French -- moderate intermediate proficiency}
\cvlistitem{(Brazilian) Portuguese -- moderate intermediate proficiency}
\cvlistitem{Spanish -- low intermediate proficiency}
\cvlistitem{Mandarin Chinese -- one year college instruction}
\subsection{Computing}
\cvlistitem{Excel -- advanced}
\cvlistitem{E-Prime -- low intermediate}
\cvlistitem{HTML -- low intermediate}
\end{document}